Percolation Analysis – Building a Package

### 2020-04-21 README.Rmd
added vignette information + renamed vignette to be easier found
corrected order of parameters in readme

_percolate(data, distance_table = NULL, limit, radius_unit, upper_radius, lower_radius, step_value)_

@@

*ID1* and *ID2* are point IDs (i.e. the PlcIndex values) and

*d12* denotes the weighted distance between them, if a non-euclidian distance is whished to be used.

@@

*percolate(data = database,, limit = 50, radius_unit = 1000, upper_radius = 40, lower_radius = 2, step_value = 1)*

>>>>

_percolate(data, distance_table = NULL, upper_radius, lower_radius, step_value, limit, radius_unit)_

@@

*ID1* and *ID2* are point IDs (i.e. the PlcIndex values) and *d12* denotes the weighted distance between them, if a non-euclidian distance is whished to be used.

@@

*percolate(data = database,, upper_radius = 40, lower_radius = 2, step_value = 1, limit = 50, radius_unit = 1000)*
